Adolescent well-being in the digital age

### 2022-01-10 00-clean.qmd
Split into sections

---
title: "Adolescent well-being in the digital age"
author: "Matti Vuorre"
execute:
  enabled: true
  cache: true
  warning: false
  message: false
format: 
  html:
    monofont: Fira Code
    font-size: 1.0em
    code-fold: true
toc: true
toc-depth: 4
crossref:
  fig-prefix: Figure
  tbl-prefix: Table
---

```{r document-options, include = FALSE, cache = FALSE}
# knitr options
knitr::opts_chunk$set(
  fig.align = "center",
  cache.lazy = FALSE # Fix large knitr cache
)
```

## Preface

Welcome! This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation). It contains all the analyses reported in the manuscript along with supplemental analyses. The source code and the underlying data are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), with an archived permanent copy on [OSF](https://osf.io/ys7m9/).

::: {.callout-note collapse="true"}
### Reproducibility

The analyses were conducted in R, and can be reproduced locally:

1.  Clone the github repo

-   Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`
-   RStudio: File -> New Project -> Version Control -> Git -> use the URL from above

2.  Prepare the R environment

-   Terminal: `Rscript -e "renv::restore()`
-   RStudio: Click renv -> Restore Library in the Packages panel

3.  Render `index.qmd` to `index.html`

-   Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
-   Terminal: `quarto render index.qmd`
-   RStudio: Open `index.qmd` and click Render

The models take several hours each to run---depending on your local computing resources---and therefore the rendering process can take several days.

If something doesn't work please open an issue at <https://github.com/digital-wellbeing/global-wbmh/issues>.
:::

## Data preparation

Our analyses draw on three sources of data. The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021. The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019. And finally the International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.

In this first section, we load the raw data sets and prepare them for analyses. We first set up the R environment with these packages and settings:

```{r setup, cache = FALSE}

# Packages
library(readxl)
library(knitr)
library(ragg)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(labelled)
library(countrycode)
library(ggtext)
library(dtplyr)
library(lubridate)
library(kableExtra)
library(gtsummary)
library(ggstance)
library(mgcv)
library(brms)
library(cmdstanr)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(kableExtra)
library(tidyverse)

# MCMC settings (ensure at most 12 cores)
ncores <- min(parallel::detectCores(logical = FALSE), 12)
nchains <- 4
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = nchains,
  cores = nchains,
  threads = ncores %/% nchains,
  iter = 2500,
  warmup = 1000,
  refresh = 50,
  adapt_delta = .90,
  max_treedepth = 10
)

# Plotting theme & use this font if available
Font <- "Titillium Web"
theme_set(
  theme_linedraw(
    base_size = 12,
    base_family = Font
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
    )
)

#' Custom kableExtra formatting
#'
#' @param a table from kbl()
#'
#' @return a table
kable_custom <- function(x) {
  kable_classic(
    kable_input = x,
    html_font = Font,
    font_size = 13,
    lightable_options = "striped",
    position = "center",
    full_width = FALSE
  )
}

# Create directory for intermediate files
dir.create("models", FALSE)
```

### Gallup World Poll

We first prepare the Gallup data. Note that this data set is not publicly available, and therefore not included in our repository. We provide a synthetic mock dataset---loaded below---for users who do not have access to the GWP dataset.

@@

```{r gwp-harmonise-countries}
#| results: hold
#| label: tbl-gwp-countries
#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing"
#| layout-ncol: 1

# Check what names were changed and if any don't have harmonised counterpart
gwp %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "GWP harmonised country names") %>%
  kable_custom()

@@

### Global Burden of Disease

We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`. We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/): We load all the GBD tables to R. They are inside downloaded `.zip` files, of which there may be more than one.

@@

# Check what names were changed and if any don't have harmonised counterpart
gbd %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "GBD harmonised country names") %>%
  kable_custom()
# Harmonise old names and replace only if harmonised name found
gbd <- gbd %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)
```

### International Telecommunication Union

After processing the outcome tables above, we move on to the internet adoption metrics from the ITU. We downloaded these data files from the ITU website. New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.

@@

```{r itu-process}
#| results: hold
#| label: tbl-itu-0
#| tbl-cap: "ITU countries"
#| layout-ncol: 1

@@

# Harmonise countries
# Check what names were changed and if any don't have harmonised counterpart
itu %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "ITU harmonised country names") %>%
  kable_custom()

@@

### GLOBE regions

@@

### ITU summary table

```{r itu-summary-table}
#| column: page
#| tbl-cap: "Mean internet user percentages across regions and time."
#| label: tbl-itusummary

@@

## RQ1: Time courses

Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)? And, do changes in well-being correlate with changes in internet adoption (RQ1b)? To answer, we estimate a multilevel multivariate model of the outcomes and internet adoption.

### Modelling

We first prepare the variables for modelling:

-   Transform edge values of internet variable to fit beta
    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
-   Join outcome and predictor tables
-   Center year on 2010 (roughly in the middle)
-   Ensure that age and sex are treated with contrast codes

```{r model1-prepare-data}
# Transform internet edge cases
itu <- itu %>%
  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
  mutate(internet = if_else(internet == 1, .9999999, internet))

# Stack outcome data
dat <- bind_rows(gwp, gbd)

# Merge predictors to outcomes
dat <- left_join(dat, itu)

# Center and scale year
dat <- dat %>%
  mutate(year = (year - 2010) / 10)

# Identify values to use in mv models
# Indicate unique ITU values for MV model
dat <- dat %>%
  # Unique values exist for each country-year, but must be given for each
  # outcome
  group_by(region, country, year, outcome) %>%
  mutate(itu = 1:n() == 1) %>%
  ungroup()

# Ensure that factors are contrast coded
dat <- dat %>%
  mutate(across(c(sex, age), factor))
options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))

# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
dat <- dat %>%
  mutate(across(c(val, se), ~ . * 100))

# Arrange on outcome
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
dat <- dat %>%
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(dat, outcome, region, country, year)

dat %>%
  group_by(outcome) %>%
  summarise(
    min = min(val, na.rm = TRUE),
    max = max(val, na.rm = TRUE),
    internet_min = min(internet, na.rm = TRUE),
    internet_max = max(internet, na.rm = TRUE)
  ) %>%
  kable(digits = 7) %>% 
  kable_custom()
```

#### Specification

We first tackle RQ1: To what extent did the outcomes change over time (1a), and were changes in outcomes correlated with changes in internet adoption between countries (1b). Model 1, a three-level bayesian meta-regression model, will provide answers, by simultaneously estimating trends over time for the outcome (e.g. Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries. We also include contrast-coded demographic factors as main effects and moderators, and can therefore examine whether the trends differ between demographic groups (RQ3)

We fit the model separately for each outcome. Although a full multivariate would additionally allow examining correlations in time trends of the outcomes, it is not plausible with the differential groups in the data sets (contrast coded demographic groups would be harder to interpret). We therefore estimate six separate bivariate models

In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian. All the regression coefficients are allowed to vary randomly across regions and countries, with a shared correlation matrix of the random effects across the two model outcomes. This latter specification is important to allow answering RQ1b.

The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate. For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age). The one downside of this modelling strategy is that it does not converge for self-harm, probably because the means and SEs are highly correlated in those data. Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero, leading to a regular (three-level) regression model.

We write the model as

$$
\begin{align*}
y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2y}v_i) \\
\mu^y_i &= \beta^{y}_{0} + \delta^{y}_{0\text{region}[i]} + 
\gamma^{y}_{0\text{country}[i]} + \\ &(\beta^y_{1} + \delta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]})\text{Time}_i + 
\\ &(\beta^y_{2} + \delta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]})\text{Sex}_i + 
\\ &(\beta^y_{3} + \delta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]})\text{Age}_i + 
\\ &(\beta^y_{4} + \delta^{y}_{4\text{region}[i]} + \gamma^{y}_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
\\ &(\beta^y_{5} + \delta^{y}_{5\text{region}[i]} + \gamma^{y}_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i \\ \\
x_i &\sim \text{Beta}(\mu^x_i, \phi^x) \\ 
\text{logit}(\mu^x_i) &= \beta^{y}_{0} + \delta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + \\ &(\beta^x_{1} + \delta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
\left[\begin{array}{c}
\delta^y_{0\text{region}} \\ \delta^y_{1\text{region}} \\ 
\delta^y_{2\text{region}} \\ \delta^y_{3\text{region}} \\ 
\delta^y_{4\text{region}} \\ \delta^y_{5\text{region}} \\ 
\delta^x_{0\text{region}} \\ \delta^x_{1\text{region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{r}
),
\left[\begin{array}{c}
\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\ 
\gamma^y_{4\text{country}} \\ \gamma^y_{5\text{country}} \\ 
\gamma^x_{0\text{country}} \\ \gamma^x_{1\text{country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{c}
)
\end{align*}
$$

Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances.

We then define the model formulas in brms' formula syntax. First, for internet adoption, we take care to indicate that each internet adoption datum should be modelled only once, because the values are repeated in the outcome data table. To do this we use `resp_subset(itu)`, where `itu` indicates first unique rows of ITU data in the model. The `|c|` and `|r|` separating the random effects from their grouping factors indicate shared correlation matrices with other modelled parameters in the model (see the next model formula below).

```{r model1-itu-bf}
# Define a model of internet proportion over year
bf_itu <- bf(
  internet | resp_subset(itu) ~
  year +
    (year |c| country) +
    (year |r| region),
  family = Beta()
)
```

Here, we specify the outcome model. Note the `|c|` and `|r|` that link the countries' and regions', respectively, random effects of this model with the previous' model. Then, we specify `resp_se(se, sigma = TRUE)` to enable "meta-regression" with known standard errors. In addition, it leads to the residual variance to be estimated.

```{r model1-val-bf}
# Meta-regression model of outcomes
bf_1 <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age +
    (year * sex + year * age | c | country) +
    (year * sex + year * age | r | region),
  family = gaussian()
)
```

Finally, after numerous attempts we were unable to fit a model with meta-analytic standard errors with self-harm as the outcome in a way that would have converged. We therefore effectively removed the SEs from self-harm by setting them to zero

```{r model1-selfharm-se}
dat <- dat %>% 
  mutate(se = if_else(outcome == "Selfharm", 0, se))
```

#### Fitting

We then create a table where each row is a dataset and a model to be fitted, and then fit the models row-by-row. This takes about a day for the six outcomes.

```{r fit-model-1}
fits <- dat %>%
  # Could nest but need this to include group key in nested tibble
  group_by(outcome) %>%
  summarise(data = list(cur_data_all()))

fits <- fits %>%
  mutate(
    fit1 = map2(
      data, outcome,
      ~brm(
        formula = bf_itu + bf_1 + set_rescor(FALSE),
        data = .x,
        chains = hmc$chains,
        cores = hmc$cores,
        threads = hmc$threads,
        iter = hmc$iter,
        warmup = hmc$warmup,
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta,
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("models/brm-{.y}-1-internet")
      )
    )
  )
```

#### Summary

Here is a summary of the data modelled for each outcome

```{r model-1-data-summary}
#| column: body-outset
#| tbl-cap: "Summaries of data included in Model 1"
#| label: tbl-m1-data

#' Model summary
#'
#' @param x a brmsfit
#'
#' @return A tibble with information on data in the model
msum <- function(x) {
  tibble(
    regions = ngrps(x)$region,
    countries = ngrps(x)$country,
    `year/country` = x$data %>%
      distinct(country, year) %>%
      count(country) %>%
      pull(n) %>%
      median(),
    nobs_internet = standata(x)$N_internet,
    nobs_outcome = standata(x)$N_val,
    outcome_range = str_glue(
      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
    )
  )
}

fits %>%
  mutate(summary = map(fit1, msum)) %>%
  select(outcome, summary) %>%
  unnest(summary) %>%
  kbl(caption = "Model 1 data summary") %>%
  kable_custom() %>% 
  row_spec(0, bold = TRUE)
```

#### Model checking

Now that the models are fit we proceed to check them. We only do this for the "prototypical" model 1, and so can discard the rest for the rest of this section

##### MCMC diagnostics

First we take a look at numeric summaries of convergence and posterior effective sample sizes. The former should approach 1, the latter should approach the number of hmc iterations.

We can see that the models have converged nicely, apart from the self-harm outcome.

```{r model-1-diagnostics}
#| results: hold
#| label: tab-model1-diagnostic
#| tbl-cap: "HMC Diagnostics, Model 1 population-level regression coefficients and country-level (co)variance parameters."
#| column: body-outset

diagnostic_table <- function(fit, rx, cp) {
  diag_1 <- fits %>%
    select(fit = {{ fit }}, outcome) %>% 
    mutate(
      out =
        map(
          fit,
          ~ as_draws_df(., variable = {{ rx }}, regex = TRUE) %>%
            summarise_draws(samples = length, default_convergence_measures())
        )
    ) %>%
    select(outcome, out) %>%
    unnest(out)
  diag_1 %>%
    kbl(
      caption = cp,
      digits = c(0, 0, 0, 2, 0, 0)
    ) %>%
    column_spec(
      4,
      color = "white",
      background = spec_color(
        log(diag_1$rhat),
        direction = 1,
        option = "C",
        end = .6
      )
    ) %>%
    column_spec(
      c(5, 6),
      color = "white",
      background = spec_color(
        log(diag_1$ess_tail / diag_1$samples),
        direction = 1,
        option = "C",
        end = 0,
        begin = .6
      )
    ) %>%
    kable_custom()
}
diagnostic_table(
  fit1,
  rx = c("^b_", "^sd_", "^cor_country__internet_year__val_year$"),
  cp = "Model 1 MCMC diagnostics."
) %>% 
  scroll_box(height = "300px")
```

##### Posterior predictive check

We then take a coarse look at how well the models reproduce the input data.

```{r ppcheck-density}
#| column: page
#| fig-cap: "Graphical posterior predictive check by region (Model 1). Thin red lines indicate model replicates, whereas the blue lines indicate data; the model is mostly in smooth agreement with data, but has greater discrepancies in some regions (e.g. Anglo Depression)."
#| label: fig-ppcheck-1

ppcheck_1 <- fits %>%
  group_by(outcome) %>%
  mutate(
    out = map(
      fit1,
      ~ pp_check(
        .x,
        ndraws = 10,
        type = "dens_overlay_grouped",
        group = "region",
        resp = "val",
        newdata = .x$data
      )[[1]]
    )
  ) %>%
  ungroup() %>% 
  select(outcome, out) %>%
  unnest(out)

ppcheck_1 %>%
  ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
  scale_color_brewer(palette = "Set1") +
  scale_alpha_manual(values = c(.2, 1)) +
  stat_density(
    geom = "line",
    size = .75,
    position = position_identity()
  ) +
  labs(x = "Value", y = "Density") +
  facet_grid2(
    outcome ~ group,
    scales = "free", independent = "x",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    legend.position = "none",
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )
rm(ppcheck_1)
```

### Results

#### RQ1a: Temporal trends

Before presenting the time trends, we must calculate the required quantities from the posterior distribution. Here we calculate posterior *samples* of region and average-level trends over time, and posterior *summaries* of trends at all levels.

```{r calculate-simple-effects}
#' Posterior draws at average and region levels
#'
#' @param x brmsfit (model 1/2)
#' @param p name of parameter
#'
#' @return a long tibble posterior draws of p for every region (including the average, so useful for e.g. forest plots)
pdraws <- function(x, p = "val_year") {
  bind_cols(
    tibble("Average" = fixef(x, summary = FALSE)[, p]),
    as_tibble(coef(x, summary = FALSE)$region[, , p])
  ) %>%
    pivot_longer(everything(), names_to = "region")
}

#' Posterior summaries at country- region- and average levels
#'
#' @param x brmsfit (model 1/2)
#' @param p name of parameter
#'
#' @return a long tibble with posterior summary of p at each level
psums <- function(x, p = "val_year") {
  psum_region <- bind_rows(
    fixef(x) %>%
      as.data.frame() %>%
      rownames_to_column("parameter") %>%
      filter(parameter == {{ p }}) %>%
      select(-parameter) %>%
      mutate(region = "Average"),
    coef(x)$region[, , p] %>%
      as.data.frame() %>%
      rownames_to_column("region")
  ) %>%
    as_tibble()

  psum_country <- ranef(x)$country[, , p] %>%
    as.data.frame() %>%
    rownames_to_column("country") %>%
    left_join(distinct(x$data, region, country)) %>%
    as_tibble() %>%
    left_join(select(psum_region, region, r_value = Estimate)) %>%
    mutate(across(Estimate:Q97.5, ~ . + r_value)) %>%
    select(-r_value)

  bind_rows(
    psum_region,
    psum_country
  ) %>%
    mutate(region = fct_relevel(region, "Average"))
}

p_draws <- fits %>%
  mutate(pdraws = map(fit1, pdraws)) %>%
  select(outcome, pdraws) %>%
  unnest(pdraws) %>%
  mutate(region = fct_relevel(region, "Average"))
p_sums <- fits %>%
  mutate(psums = map(fit1, psums)) %>%
  select(outcome, psums) %>%
  unnest(psums) %>%
  mutate(region = fct_relevel(region, "Average"))
p_sums_internet <- fits %>%
  mutate(psums = map(fit1, ~ psums(.x, "internet_year"))) %>%
  select(outcome, psums) %>%
  unnest(psums) %>%
  mutate(region = fct_relevel(region, "Average"))
```

We then display the average ($\beta^y_1$), region- ($\delta^y_1$), and country-level ($\gamma^y_1$) time trend parameters' posterior distributions. Recall the scales of the variables when interpreting the magnitudes: Year is in decades and outcomes are percentages (0-100).

```{r forest-trends}
#| column: screen-inset
#| fig-width: 14
#| fig-height: 9
#| fig-cap: "Forest plot of linear trends in outcomes"
#| label: fig-forest-trends
p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Estimated linear change per decade",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x",
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
```

@fig-forest-trends shows, starting from the top left panel, the average (across countries and regions) change in life satisfaction. This change is not credibly different from zero, at the 95% credibility level, and the posterior mean value of change was a 1% increase in life satisfaction per decade. The region-specific changes were likewise not credibly different from zero, apart from the Eastern Europe region that indicated a modest increase in life satisfaction.

Because we modelled regions (and countries) as draws from a multivariate normal prior distribution, the region-specific estimates are shrunk toward the overall mean and therefore less likely to overfit any individual region's data. This means that the model is less likely to report "false alarms", or estimates at the region- and country-levels that indicate false certainty in nonzero changes. Therefore, although there are a large number of change parameters for each individual outcome, we can be fairly certain that the observed change in Eastern Europe is not due to sampling error but represents a real trend in that population.

We observe credible increases in negative experiences in more regions, with notably a \~10% increase per decade in the African region. However, the average change again is not credibly different from zero. Positive experiences had increased, both on average and across 7/10 regions, with very similar changes in Anxiety. Depression and self-harm, on the other hand, had decreased across the board.

In sum these results were somewhat mixed, where some regions showing both increases (e.g. decreased depression) and decreases (increased anxiety) in well-being.

Then to help illustrate the parameters, we draw figures of the fitted lines conditional on the predictors, or so called counterfactual plots.

```{r fitted-trend-country}

#' Get (grand mean) fitted values for countries
#'
#' @param x a brmsfit model 1
#'
#' @return a data frame of fitted values
fitted_country <- function(x) {
  newx <- x$data %>%
    group_by(country, region, outcome, year) %>%
    summarise(val = mean(val, na.rm = TRUE)) %>%
    ungroup() %>%
    mutate(sex = NA, age = NA, se = 0)
  newy <- bind_cols(
    newx,
    as.data.frame(fitted(x, newdata = newx, resp = "val"))
  ) %>%
    select(-outcome)
  newy
}

f_country <- fits %>%
  mutate(fc = map(fit1, fitted_country)) %>%
  select(outcome, fc)

#' Draw a panel plot of countries' fitted values and data
#'
#' @param x fitted country level data from fitted_country()
#' @param y outcome
#'
#' @return a ggplot for that outcome
plot_country <- function(x, y) {
  coefs <- p_sums %>%
    drop_na(country) %>%
    filter(outcome == y) %>%
    select(country, coef = Estimate, coef.l = Q2.5, coef.u = Q97.5) %>%
    mutate(country = fct_reorder(country, coef))
  x %>%
    left_join(coefs) %>%
    mutate(country = fct_reorder(country, coef)) %>%
    ggplot(aes(make_date(year * 10 + 2010), Estimate)) +
    scale_x_date("Year", date_breaks = "5 years", date_labels = "'%y") +
    scale_y_continuous(
      str_replace(y, "_", " "),
      breaks = pretty_breaks(),
      expand = expansion(.15),
      labels = function(x) {
        percent(x / 100, .01) %>%
          str_remove("\\.00")
      }
    ) +
    # Add parameters in text
    geom_richtext(
      data = coefs %>%
        mutate(across(where(is.numeric), ~ number(., .01))),
      aes(
        x = make_date(2000), y = Inf,
        label = str_glue("{coef}<br>[{coef.l}, {coef.u}]")
      ),
      size = 2.4, vjust = 1, hjust = 0.05, color = "black",
      family = Font,
      fill = alpha("white", .3), label.color = NA,
      label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines")
    ) +
    geom_point(aes(y = val), shape = 1, alpha = .5) +
    geom_ribbon(
      aes(ymin = Q2.5, ymax = Q97.5),
      alpha = .3, col = NA, fill = "dodgerblue1"
    ) +
    geom_line(
      size = 0.5, col = "dodgerblue1"
    ) +
    facet_wrap(
      "country"
    ) +
    theme(panel.spacing = unit(2, "pt"))
}

# Create the plot for each outcome
f_country <- f_country %>%
  mutate(
    plot = map2(
      fc, outcome,
      ~ plot_country(.x, .y)
    )
  )
```

::: {.panel-tabset .column-screen-inset-shaded}
##### All outcomes

```{r trends-regions}
#| echo: false
#| fig-width: 14
#| fig-height: 9
#| fig-cap: "Trends in all variables across regions"
#| label: fig-trends-regions

# Stack data sets
# Assume all outcomes are proportions (0-1)
dat_all <- bind_rows(
  gwp,
  gbd,
  itu %>% mutate(outcome = "Internet", val = internet)
) %>%
  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
  group_by(region, country, year, outcome) %>%
  summarise(mean = mean(val, na.rm = TRUE)) %>%
  ungroup()

# Draw small multiples figure, outcomes x regions
dat_all %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    date_breaks = "5 years",
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, outcome)),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line",
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "none",
    panel.spacing = unit(3, "pt"),
    axis.title.y = element_blank()
  )
```

##### Life satisfaction

```{r trends-ls}
#| echo: false
#| fig-width: 16
#| fig-height: 12
#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
#| label: fig-trends-ls
f_country$plot[[1]]
```

##### Negative experiences

```{r trends-ne}
#| echo: false
#| fig-width: 16
#| fig-height: 12
#| fig-cap: "Negative experiences trends, ordered by association magnitude"
#| label: fig-trends-ne
f_country$plot[[2]]
```

##### Positive experiences

```{r trends-pe}
#| echo: false
#| fig-width: 16
#| fig-height: 12
#| fig-cap: "Positive experiences trends, ordered by association magnitude"
#| label: fig-trends-pe
f_country$plot[[3]]
```

##### Anxiety

>>>>

# Data preparation {.unnumbered}

```{r setup}
#| cache: false
# Packages
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(labelled)
library(countrycode)
library(lubridate)
library(gtsummary)
library(kableExtra)
library(tidyverse)

# Create directory for intermediate files
dir.create("data", FALSE)
```

In this first section, we load the raw data sets and prepare them for analyses.

## Gallup World Poll

We first prepare the Gallup data. The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021.

Note that this data set is not publicly available, and therefore not included in our repository. We provide a synthetic mock dataset for researchers who would like to reproduce our analyses but do not have access to the GWP dataset.

@@

```{r gwp-harmonise-countries}
#| results: hold
#| label: tbl-gwp-countries
#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing and therefore the original name is retained."

# Check what names were changed and if any don't have harmonised counterpart
gwp %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "GWP country names") %>%
  kable_custom()

@@

We then load the synthetic GWP dataset if the real data was not found. This is just a list of the countries, years and demographics in the actual data, with gaussian noise for the outcomes' mean and SE values.

```{r}
# Create if doesn't exist
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (!file.exists(gwp_mock_path)) {
  distinct(gwp, outcome, country, year, sex, age) %>% 
    mutate(
      se = rnorm(
        nrow(.), 
        mean(gwp$se, na.rm = TRUE), 
        sd(gwp$se, na.rm = TRUE)
      ),
      val = rnorm(
        nrow(.), 
        mean(gwp$val, na.rm = TRUE), 
        sd(gwp$val, na.rm = TRUE)
      )
    ) %>% 
    write_rds(gwp_mock_path, compress = "xz")
}
# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```

## Global Burden of Disease

The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019.

We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`. We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/). They are inside downloaded `.zip` files, of which there may be more than one (depending on the download size). Here, we load those tables to R.

@@

# Check what names were changed and if any don't have harmonised counterpart
gbd %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "GBD country names") %>%
  kable_custom()
# Harmonise old names and replace only if harmonised name found
gbd <- gbd %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)
```

## International Telecommunication Union

After processing the outcome tables above, we move on to the internet adoption metrics from the ITU. The International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.

We downloaded the data files from the ITU website. New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.

@@

```{r itu-process}
#| results: hold
#| label: tbl-itu-0
#| tbl-cap: "Countries whose original ITU name is different to the harmonised one, or whose harmonised name is missing"
#| layout-ncol: 1

@@

# Harmonise countries
# Check what names were changed and if any don't have harmonised counterpart
itu %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "ITU country names") %>%
  kable_custom()

@@

## GLOBE regions

@@

## ITU summary table

```{r itu-summary-table}
#| column: page-right
#| tbl-cap: "Mean internet user percentages across regions and time."
#| label: tbl-itusummary

@@

## Write data tables

We have organised our code into separate files, and so save the processed data here for use in the other analysis scripts.

```{r}
write_rds(itu, "data/itu.rds")
write_rds(gwp, "data/gwp.rds")
write_rds(gbd, "data/gbd.rds")
```
